---
title: "Peak power and energy - 1 Aldrich St"
format:
  html:
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libs}
library(tidyverse)
library(gt)
library(solaredge)

```

This report details some concerns about the power generation of the 
solar array installed at 1 Aldrich St, Northampton, and activated 
April 7, 2023.

## Peak power

The designed maximum power generation of the system is just over 6kW. 
On the first three full days of operation, peak power of 6kW was sustained for several hours each day with over 45kWh generated each day.

This chart shows power clearly peaking at 6kW on April 8-10. April 20
comes close to this performance but does not match it.

```{r april_power}
power_chart('2023-04-10')
```

This level of performance has not been seen again in the six months 
the system has been operating.
Eleven days in April hit 6kW power at some point during the day. 
This happened only three times in May, once in June, not at all in July
and twice in August.

```{r daily_max, fig.width=9}
daily_max_power_chart()
```

# Daily energy

A similar story is told by daily total energy production. April 8-10 saw
more than 45kWh generated each day; this level has never been reached again.

May saw thirteen days with more than 40kWh generation; this level was not
reached at all in June and July, only three times in August, and once 
in September.

```{r daily_energy, fig.width=9}
daily_energy_chart()
```

# Actual vs predicted

Comparing actual monthly energy generation with the predictions in the PV Squared
proposal, May greatly exceeded the prediction; all subsequent months fell
short.

```{r actual_vs_predicted}
monthly_energy_chart() +
  scale_x_continuous(breaks=5:10, labels=month.abb[5:10], limits=c(4,11))

energy = energy_table() |> 
  group_by(year, month) |> 
  summarize(kWh = sum(value)/1000, .groups='drop') |> 
  collect() |> 
  rename(Month=month) |> 
  filter(!Month %in% c(4, 11))

prediction = monthly_predictions() |> filter(Month %in% energy$Month)

prediction |> 
  left_join(energy, by='Month', suffix=c('.Predicted', '.Actual')) |> 
  mutate(kWh.Difference=kWh.Actual-kWh.Predicted,
         Month=month.name[Month],
         'Percent difference'=kWh.Difference/kWh.Predicted) |> 
  select(-year) |> 
  gt() |>
  grand_summary_rows(columns=2:4, 
                     fns=list(label='Total') ~ sum(.),
                     fmt=~fmt_number(., decimals=0),
                     missing_text='') |> 
  fmt_number(columns=2:4, decimals=0) |> 
  fmt_percent(columns=5, decimals=0) |> 
  tab_spanner_delim('.') |> 
  tab_header(title='Actual and predicted energy generation', 
    subtitle='1 Aldrich St, 2023')

```

