---
title: "Power and energy"
format:
  html:
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libs}
library(tidyverse)
library(solaredge)

```

## Peak power

The designed maximum power generation of the system is just over 6kW. 
On the first three full days of operation, peak power of 6kW was sustained for several hours each day with over 45kWh generated each day.

This chart shows power clearly peaking at 6kW on April 8-10. April 20
comes close to this performance but does not match it.

```{r april_power}
power_chart('2023-04-10')
```

This level of performance has not been seen again in the three months 
the system has been operating.

Eleven days in April hit 6kW power at some point during the day. This happened only twice in May and once in April.

```{r daily_max}
daily_max_power_chart()
```

# Daily energy

A similar story is told by daily total energy production. April 8-10 saw
more than 45kWh generated each day; this level has never been reached again.

May saw thirteen days with more than 40kWh generation; this level has not been
reached since. The maximum to date in July is 37kWh.

```{r daily_energy}
daily_energy_chart()
```

